Ground state energy of quantum dots using the coupled cluster method

### 2018-06-07 project_2/article/article.tex

        \begin{table}
            \centering
            \caption{Here we look at $N = 12$ particles ($R = 3$ shells).  We did
            not achieve convergence using the harmonic oscillator basis for the
            lower frequency values and large number of shells. No convergence is
            marked as {\nan} in the table.}
            \begin{ruledtabular}
                \begin{tabular}{c|c|ccc}
                    $\omega$ & $R$ & RHF & CCD(HO) & CCD(HF) \\
                    \hline
                          & $3$ & $46.361130$ & $46.361130$ & $46.361130$ \\
                          & $4$ & $43.663267$ & $45.837079$ & $43.309845$ \\
                          & $5$ & $41.108851$ & $45.456883$ & $40.654710$ \\
                          & $6$ & $40.750512$ & \nan & $40.068340$ \\
                    $0.5$ & $7$ & $40.302719$ & \nan & $39.508500$ \\
                          & $8$ & $40.263752$ & \nan & $39.399128$ \\
                          & $9$ & $40.216688$ & \nan & $39.329311$ \\
                          & $10$ & $40.216252$ & \nan & $39.309409$ \\
                          & $11$ & $40.216195$ & \nan & $39.296007$ \\
                          & $12$ & $40.216165$ & \nan & $39.285968$ \\
                    \hline
                          & $3$ & $73.765549$ & $73.765549$ & $73.765549$ \\
                          & $4$ & $70.673849$ & $73.314476$ & $70.324250$ \\
                          & $5$ & $67.569930$ & $72.990679$ & $67.031096$ \\
                          & $6$ & $67.296869$ & \nan & $66.526677$ \\
                    $1.0$ & $7$ & $66.934745$ & \nan & $66.049564$ \\
                          & $8$ & $66.923094$ & \nan & $65.972157$ \\
                          & $9$ & $66.912244$ & \nan & $65.921205$ \\
                          & $10$ & $66.912035$ & \nan & $65.889281$ \\
                          & $11$ & $66.911365$ & \nan & $65.866715$ \\
                          & $12$ & $66.911364$ & \nan & $65.849776$ \\
                    \hline
                          & $3$ & $120.722260$ & $120.722260$ & $120.722260$ \\
                          & $4$ & $117.339642$ & $120.296556$ & $116.995036$ \\
                          & $5$ & $113.660396$ & $120.007146$ & $113.048934$ \\
                          & $6$ & $113.484866$ & $119.759037$ & $112.658821$ \\
                    $2.0$ & $7$ & $113.247601$ & $119.662199$ & $112.309482$ \\
                          & $8$ & $113.246579$ & $119.584733$ & $112.235521$ \\
                          & $9$ & $113.246303$ & $119.524394$ & $112.181828$ \\
                          & $10$ & $113.245854$ & $119.472283$ & $112.140661$ \\
                          & $11$ & $113.245256$ & $119.430353$ & $112.109973$ \\
                          & $12$ & $113.245183$ & $119.394712$ & $112.085683$ \\
                    \hline
                    $5.0$ & $3$ & $242.334879$ & $242.334879$ & $242.334879$ \\
                          & $4$ & $238.739591$ & $241.927593$ & $238.394598$ \\
                          & $5$ & $234.352741$ & $241.663950$ & $233.680649$ \\
                          & $6$ & $234.282331$ & $241.507595$ & $233.425243$ \\
                          & $7$ & $234.194820$ & $241.390525$ & $233.226529$ \\
                          & $8$ & $234.194059$ & $241.293417$ & $233.137933$ \\
                          & $9$ & $234.190797$ & $241.221056$ & $233.070205$ \\
                          & $10$ & $234.190714$ & $241.158896$ & $233.020009$ \\
                          & $11$ & $234.190665$ & $241.109926$ & $232.980634$ \\
                          & $12$ & $234.190553$ & $241.068091$ & $232.948528$
                \end{tabular}
            \end{ruledtabular}
            \label{tab:N12}
        \end{table}

        \begin{table}
            \centering
            \caption{In this table we look at $N = 20$ particles ($R = 4$
            shells).  We did not achieve convergence using the harmonic
            oscillator basis for the lower frequency values and large number of
            shells. No convergence is marked as {\nan} in the table.}
            \begin{ruledtabular}
                \begin{tabular}{c|c|ccc}
                    $\omega$ & $R$ & RHF & CCD(HO) & CCD(HF) \\
                    \hline
                    $1.0$ & $4$ & $177.963297$ & $177.963297$ & $177.963297$ \\
                          & $5$ & $168.792442$ & $177.206536$ & $168.459124$ \\
                          & $6$ & $161.339721$ & \nan & $160.594507$ \\
                          & $7$ & $159.958722$ & \nan & $158.841120$ \\
                          & $8$ & $158.400172$ & \nan & $157.038330$ \\
                          & $9$ & $158.226030$ & \nan & $156.676039$ \\
                          & $10$ & $158.017667$ & \nan & $156.367930$ \\
                          & $11$ & $158.010276$ & \nan & $156.292422$ \\
                          & $12$ & $158.004951$ & \nan & $156.238258$ \\
                    \hline
                    $2.0$ & $4$ & $286.825295$ & $286.825295$ & $286.825295$ \\
                          & $5$ & $276.898196$ & $286.159148$ & $276.381708$ \\
                          & $6$ & $267.269712$ & $285.614958$ & $266.413122$ \\
                          & $7$ & $266.213200$ & \nan & $264.969415$ \\
                          & $8$ & $264.933622$ & \nan & $263.434546$ \\
                          & $9$ & $264.874009$ & \nan & $263.215451$ \\
                          & $10$ & $264.809954$ & \nan & $263.046195$ \\
                          & $11$ & $264.809901$ & \nan & $262.963703$ \\
                          & $12$ & $264.809306$ & \nan & $262.899698$ \\
                    \hline
                    $5.0$ & $4$ & $563.773952$ & $563.773952$ & $563.773952$ \\
                          & $5$ & $552.630093$ & $563.160136$ & $552.118708$ \\
                          & $6$ & $540.804720$ & $562.692231$ & $539.824400$ \\
                          & $7$ & $540.227793$ & $562.306123$ & $538.886074$ \\
                          & $8$ & $539.499326$ & $562.114279$ & $537.925127$ \\
                          & $9$ & $539.495941$ & \nan & $537.769045$ \\
                          & $10$ & $539.494611$ & \nan & $537.646668$ \\
                          & $11$ & $539.493513$ & \nan & $537.548828$ \\
                          & $12$ & $539.491764$ & \nan & $537.470616$ \\
                    \hline
                    $10.0$ & $4$ & $973.032700$ & $973.032700$ & $973.032700$ \\
                           & $5$ & $961.371081$ & $972.439478$ & $960.862053$ \\
                           & $6$ & $948.057077$ & $972.002302$ & $947.019789$ \\
                           & $7$ & $947.765474$ & $971.716015$ & $946.399546$ \\
                           & $8$ & $947.410305$ & $971.508584$ & $945.827806$ \\
                           & $9$ & $947.409440$ & $971.332133$ & $945.663820$ \\
                           & $10$ & $947.404930$ & $971.193592$ & $945.528489$ \\
                           & $11$ & $947.404361$ & $971.076617$ & $945.424175$ \\
                           & $12$ & $947.403875$ & $970.978571$ & $945.339080$ \\
                \end{tabular}
            \end{ruledtabular}
            \label{tab:N20}
        \end{table}

>>>>

        \begin{table}
            \centering
            \caption{Here we look at $N = 12$ particles ($R = 3$ shells).  We did
            not achieve convergence using the harmonic oscillator basis for the
            lower frequency values and large number of shells.}
            \begin{ruledtabular}
                \begin{tabular}{c|c|ccc}
                    $\omega$ & $R$ & RHF & CCD(HO) & CCD(HF) \\
                    \hline
                          & $3$ & $46.361130$ & $46.361130$ & $46.361130$ \\
                          & $4$ & $43.663267$ & $45.837079$ & $43.309845$ \\
                          & $5$ & $41.108851$ & $45.456883$ & $40.654710$ \\
                          & $6$ & $40.750512$ & \nan & $40.068340$ \\
                    $0.5$ & $7$ & $40.302719$ & \nan & $39.508500$ \\
                          & $8$ & $40.263752$ & \nan & $39.399128$ \\
                          & $9$ & $40.216688$ & \nan & $39.329311$ \\
                          & $10$ & $40.216252$ & \nan & $39.309409$ \\
                          & $11$ & $40.216195$ & \nan & $39.296007$ \\
                          & $12$ & $40.216165$ & \nan & $39.285968$ \\
                    \hline
                          & $3$ & $73.765549$ & $73.765549$ & $73.765549$ \\
                          & $4$ & $70.673849$ & $73.314476$ & $70.324250$ \\
                          & $5$ & $67.569930$ & $72.990679$ & $67.031096$ \\
                          & $6$ & $67.296869$ & \nan & $66.526677$ \\
                    $1.0$ & $7$ & $66.934745$ & \nan & $66.049564$ \\
                          & $8$ & $66.923094$ & \nan & $65.972157$ \\
                          & $9$ & $66.912244$ & \nan & $65.921205$ \\
                          & $10$ & $66.912035$ & \nan & $65.889281$ \\
                          & $11$ & $66.911365$ & \nan & $65.866715$ \\
                          & $12$ & $66.911364$ & \nan & $65.849776$ \\
                    \hline
                          & $3$ & $120.722260$ & $120.722260$ & $120.722260$ \\
                          & $4$ & $117.339642$ & $120.296556$ & $116.995036$ \\
                          & $5$ & $113.660396$ & $120.007146$ & $113.048934$ \\
                          & $6$ & $113.484866$ & $119.759037$ & $112.658821$ \\
                    $2.0$ & $7$ & $113.247601$ & $119.662199$ & $112.309482$ \\
                          & $8$ & $113.246579$ & $119.584733$ & $112.235521$ \\
                          & $9$ & $113.246303$ & $119.524394$ & $112.181828$ \\
                          & $10$ & $113.245854$ & $119.472283$ & $112.140661$ \\
                          & $11$ & $113.245256$ & $119.430353$ & $112.109973$ \\
                          & $12$ & $113.245183$ & $119.394712$ & $112.085683$ \\
                    \hline
                    $5.0$ & $3$ & $242.334879$ & $242.334879$ & $242.334879$ \\
                          & $4$ & $238.739591$ & $241.927593$ & $238.394598$ \\
                          & $5$ & $234.352741$ & $241.663950$ & $233.680649$ \\
                          & $6$ & $234.282331$ & $241.507595$ & $233.425243$ \\
                          & $7$ & $234.194820$ & $241.390525$ & $233.226529$ \\
                          & $8$ & $234.194059$ & $241.293417$ & $233.137933$ \\
                          & $9$ & $234.190797$ & $241.221056$ & $233.070205$ \\
                          & $10$ & $234.190714$ & $241.158896$ & $233.020009$ \\
                          & $11$ & $234.190665$ & $241.109926$ & $232.980634$ \\
                          & $12$ & $234.190553$ & $241.068091$ & $232.948528$
                \end{tabular}
            \end{ruledtabular}
            \label{tab:N12}
        \end{table}

        \begin{table}
            \centering
            \caption{In this table we look at $N = 20$ particles ($R = 4$ shells).
            We did not achieve convergence using the harmonic oscillator basis for
            the lower frequency values and large number of shells.}
            \begin{ruledtabular}
                \begin{tabular}{c|c|ccc}
                    $\omega$ & $R$ & RHF & CCD(HO) & CCD(HF) \\
                    \hline
                    $1.0$ & $4$ & $177.963297$ & $177.963297$ & $177.963297$ \\
                          & $5$ & $168.792442$ & $177.206536$ & $168.459124$ \\
                          & $6$ & $161.339721$ & \nan & $160.594507$ \\
                          & $7$ & $159.958722$ & \nan & $158.841120$ \\
                          & $8$ & $158.400172$ & \nan & $157.038330$ \\
                          & $9$ & $158.226030$ & \nan & $156.676039$ \\
                          & $10$ & $158.017667$ & \nan & $156.367930$ \\
                          & $11$ & $158.010276$ & \nan & $156.292422$ \\
                          & $12$ & $158.004951$ & \nan & $156.238258$ \\
                    \hline
                    $2.0$ & $4$ & $286.825295$ & $286.825295$ & $286.825295$ \\
                          & $5$ & $276.898196$ & $286.159148$ & $276.381708$ \\
                          & $6$ & $267.269712$ & $285.614958$ & $266.413122$ \\
                          & $7$ & $266.213200$ & \nan & $264.969415$ \\
                          & $8$ & $264.933622$ & \nan & $263.434546$ \\
                          & $9$ & $264.874009$ & \nan & $263.215451$ \\
                          & $10$ & $264.809954$ & \nan & $263.046195$ \\
                          & $11$ & $264.809901$ & \nan & $262.963703$ \\
                          & $12$ & $264.809306$ & \nan & $262.899698$ \\
                    \hline
                    $5.0$ & $4$ & $563.773952$ & $563.773952$ & $563.773952$ \\
                          & $5$ & $552.630093$ & $563.160136$ & $552.118708$ \\
                          & $6$ & $540.804720$ & $562.692231$ & $539.824400$ \\
                          & $7$ & $540.227793$ & $562.306123$ & $538.886074$ \\
                          & $8$ & $539.499326$ & $562.114279$ & $537.925127$ \\
                          & $9$ & $539.495941$ & \nan & $537.769045$ \\
                          & $10$ & $539.494611$ & \nan & $537.646668$ \\
                          & $11$ & $539.493513$ & \nan & $537.548828$ \\
                          & $12$ & $539.491764$ & \nan & $537.470616$ \\
                    \hline
                    $10.0$ & $4$ & $973.032700$ & $973.032700$ & $973.032700$ \\
                           & $5$ & $961.371081$ & $972.439478$ & $960.862053$ \\
                           & $6$ & $948.057077$ & $972.002302$ & $947.019789$ \\
                           & $7$ & $947.765474$ & $971.716015$ & $946.399546$ \\
                           & $8$ & $947.410305$ & $971.508584$ & $945.827806$ \\
                           & $9$ & $947.409440$ & $971.332133$ & $945.663820$ \\
                           & $10$ & $947.404930$ & $971.193592$ & $945.528489$ \\
                           & $11$ & $947.404361$ & $971.076617$ & $945.424175$ \\
                           & $12$ & $947.403875$ & $970.978571$ & $945.339080$ \\
                \end{tabular}
            \end{ruledtabular}
            \label{tab:N20}
        \end{table}
